Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
Stuff

\section{Related Work}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process. The main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

@@

@@

@@

\subsubsection{Extract Method} \label{sec:refactorability}
Several influencing factors may obstruct the possibility to extract code to a new method:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
    \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
    \item \textbf{Top-Level Non-Statement}: If one of the top-level AST nodes of the clone is not a statement. For instance, if a (part of) an anonymous class is cloned.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
\end{itemize}
Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CloneRefactor only refactors the clones that \textit{Can Be Extracted}.

>>>>

\section{Related Work}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored. In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.

In their work, the main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

@@

\section{Related Work}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored. In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.

In their work, the main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

@@

\begin{figure*}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doB(a);
}
\end{javacode}}
\end{parcolumns}
\caption{A clone that spans a block partially.}
\label{fig:refactorabilitypartialblock}
\end{figure*}

@@

\subsubsection{Extract Method} \label{sec:refactorability}
Several influencing factors may obstruct the possibility to extract code to a new method:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement. An example of this is shown in Fig.~\ref{fig:refactorabilitypartialblock}.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
    \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
    \item \textbf{Top-Level Non-Statement}: If one of the top-level AST nodes of the clone is not a statement. For instance, if a (part of) an anonymous class is cloned.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
\end{itemize}
Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CloneRefactor only refactors the clones that \textit{Can Be Extracted}.
